---
title: "Data collection - Bibliography"
author: "Emmanuela van Versendaal"
output: html_document
---

1) Upload the data. After searching in Scopus, ScienceDirect, and Web of Science using the keywords: Nitrogen dilution curve’ & ‘Nitrogen nutrition index’ & ‘Critical nitrogen concentration’ & the name of each crop.

2) Remove duplicates

3) Filter papers that do not contain relevant keywords and abstract information.

4) Remove papers that do not contain data of biomass or nitrogen concentration for different sampling times

5) extract figures information

# Libraries
```{r}
library(tidyverse)
library(revtools) # screening papers
library(juicr) # extract data from plots
```

# Filter per crop

## Sorghum
```{r}
Sorgum_bibliography <- read_bibliography(c("../Data/ScienceDirect_sorghum.ris",
                                           "../Data/scopus_sorghum.ris", 
                                           "../Data/WebofScience_sorghum.ciw"))
## Remove duplicates
sorghum_unique <- extract_unique_references(sorghum_bibliography, 
                                            find_duplicates(sorghum_bibliography))
## Screen and filter by title
screen_titles(sorghum_unique)
sorghum_st <- read_csv("sorghum_st.csv")
sorghum_st <- sorghum_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
sorghum_st$abstract
screen_abstracts(sorghum_st%>% as.data.frame())  

sorghum_final <- read_csv("sorghum_sa.csv")
sorghum_final <- sorghum_final %>% filter(!screened_abstracts == "excluded")
```


## Corn
```{r}
corn_bibliography <- read_bibliography(c("../Data/ScienceDirect_corn.ris",  #ScienceDirect
                                         "../Data/scopus_corn.ris",  # Scopus
                                         "../Data/WebofScience_corn.ciw")) # Web of science
## Remove duplicates
corn_unique <- extract_unique_references(corn_bibliography, 
                                         find_duplicates(corn_bibliography))
## Screen and filter by title
screen_titles(corn_unique)
corn_st <- read_csv("corn_st.csv")
corn_st <- corn_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
corn_st$abstract
screen_abstracts(corn_st%>% as.data.frame())  

corn_final <- read_csv("corn_sa.csv")
corn_final <- corn_final %>% filter(!screened_abstracts == "excluded")
```

## Rice
```{r}
rice_bibliography <- read_bibliography(c("../Data/ScienceDirect_rice.ris",  #ScienceDirect
                                         "../Data/scopus_rice.ris",  # Scopus
                                         "../Data/WebofScience_rice.ciw")) # Web of science
## Remove duplicates
rice_unique <- extract_unique_references(rice_bibliography, 
                                         find_duplicates(rice_bibliography))
## Screen and filter by title
screen_titles(rice_unique)
rice_st <- read_csv("rice_st.csv")
rice_st <- rice_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
rice_st$abstract
screen_abstracts(rice_st%>% as.data.frame())  

rice_final <- read_csv("rice_sa.csv")
rice_final <- rice_final %>% filter(!screened_abstracts == "excluded")
```

## Wheat
```{r}
wheat_bibliography <- read_bibliography(c("../Data/ScienceDirect_wheat.ris",  #ScienceDirect
                                         "../Data/scopus_wheat.ris",  # Scopus
                                         "../Data/WebofScience_wheat.ciw")) # Web of science
## Remove duplicates
wheat_unique <- extract_unique_references(wheat_bibliography, 
                                         find_duplicates(wheat_bibliography))
## Screen and filter by title
screen_titles(wheat_unique)
wheat_st <- read_csv("wheat_st.csv")
wheat_st <- wheat_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
wheat_st$abstract
screen_abstracts(wheat_st%>% as.data.frame())  

wheat_final <- read_csv("wheat_sa.csv")
wheat_final <- wheat_final %>% filter(!screened_abstracts == "excluded")
```

## Grassess
```{r}
grassess_bibliography <- read_bibliography(c("../Data/ScienceDirect_grassess.ris",  #ScienceDirect
                                         "../Data/scopus_grassess.ris",  # Scopus
                                         "../Data/WebofScience_grassess.ciw")) # Web of science
## Remove duplicates
grassess_unique <- extract_unique_references(grassess_bibliography, 
                                         find_duplicates(grassess_bibliography))
## Screen and filter by title
screen_titles(grassess_unique)
grassess_st <- read_csv("grassess_st.csv")
grassess_st <- grassess_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
grassess_st$abstract
screen_abstracts(grassess_st%>% as.data.frame())  

grassess_final <- read_csv("grassess_sa.csv")
grassess_final <- grassess_final %>% filter(!screened_abstracts == "excluded")
```

## Sugarcane
```{r}
sugarcane_bibliography <- read_bibliography(c("../Data/ScienceDirect_sugarcane.ris",  #ScienceDirect
                                         "../Data/scopus_sugarcane.ris",  # Scopus
                                         "../Data/WebofScience_sugarcane.ciw")) # Web of science
## Remove duplicates
sugarcane_unique <- extract_unique_references(sugarcane_bibliography, 
                                         find_duplicates(sugarcane_bibliography))
## Screen and filter by title
screen_titles(sugarcane_unique)
sugarcane_st <- read_csv("sugarcane_st.csv")
sugarcane_st <- sugarcane_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
sugarcane_st$abstract
screen_abstracts(sugarcane_st%>% as.data.frame())  

sugarcane_final <- read_csv("sugarcane_sa.csv")
sugarcane_final <- sugarcane_final %>% filter(!screened_abstracts == "excluded")
```

## Potato
```{r}
potato_bibliography <- read_bibliography(c("../Data/ScienceDirect_potato.ris",  #ScienceDirect
                                         "../Data/scopus_potato.ris",  # Scopus
                                         "../Data/WebofScience_potato.ciw")) # Web of science
## Remove duplicates
potato_unique <- extract_unique_references(potato_bibliography, 
                                         find_duplicates(potato_bibliography))
## Screen and filter by title
screen_titles(potato_unique)
potato_st <- read_csv("potato_st.csv")
potato_st <- potato_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
potato_st$abstract
screen_abstracts(potato_st%>% as.data.frame())  

potato_final <- read_csv("potato_sa.csv")
potato_final <- potato_final %>% filter(!screened_abstracts == "excluded")
```

## Canola and Oliseed rape
```{r}
canola_oliseed_bibliography <- read_bibliography(c("../Data/ScienceDirect_canola_oliseed.ris",  #ScienceDirect
                                         "../Data/scopus_canola_oliseed.ris",  # Scopus
                                         "../Data/WebofScience_canola_oliseed.ciw")) # Web of science
## Remove duplicates
canola_oliseed_unique <- extract_unique_references(canola_oliseed_bibliography, 
                                         find_duplicates(canola_oliseed_bibliography))
## Screen and filter by title
screen_titles(canola_oliseed_unique)
canola_oliseed_st <- read_csv("canola_oliseed_st.csv")
canola_oliseed_st <- canola_oliseed_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
canola_oliseed_st$abstract
screen_abstracts(canola_oliseed_st%>% as.data.frame())  

canola_oliseed_final <- read_csv("canola_oliseed_sa.csv")
canola_oliseed_final <- canola_oliseed_final %>% filter(!screened_abstracts == "excluded")
```

## Cotton
```{r}
cotton_bibliography <- read_bibliography(c("../Data/ScienceDirect_cotton.ris",  #ScienceDirect
                                         "../Data/scopus_cotton.ris",  # Scopus
                                         "../Data/WebofScience_cotton.ciw")) # Web of science
## Remove duplicates
cotton_unique <- extract_unique_references(cotton_bibliography, 
                                         find_duplicates(cotton_bibliography))
## Screen and filter by title
screen_titles(cotton_unique)
cotton_st <- read_csv("cotton_st.csv")
cotton_st <- cotton_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
cotton_st$abstract
screen_abstracts(cotton_st%>% as.data.frame())  

cotton_final <- read_csv("cotton_sa.csv")
cotton_final <- cotton_final %>% filter(!screened_abstracts == "excluded")
```

## Sunflower
```{r}
sunflower_bibliography <- read_bibliography(c("../Data/ScienceDirect_sunflower.ris",  #ScienceDirect
                                         "../Data/scopus_sunflower.ris",  # Scopus
                                         "../Data/WebofScience_sunflower.ciw")) # Web of science
## Remove duplicates
sunflower_unique <- extract_unique_references(sunflower_bibliography, 
                                         find_duplicates(sunflower_bibliography))
## Screen and filter by title
screen_titles(sunflower_unique)
sunflower_st <- read_csv("sunflower_st.csv")
sunflower_st <- sunflower_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
sunflower_st$abstract
screen_abstracts(sunflower_st%>% as.data.frame())  

sunflower_final <- read_csv("sunflower_sa.csv")
sunflower_final <- sunflower_final %>% filter(!screened_abstracts == "excluded")
```

## Storage root crops
```{r}
storagerootcrops_bibliography <- read_bibliography(c("../Data/ScienceDirect_beet.ris",  #ScienceDirect
                                                     "../Data/scopus_beet.ris",  # Scopus
                                                     "../Data/WebofScience_beets.ciw")) # Web of science
## Remove duplicates
storagerootcrops_unique <- extract_unique_references(storagerootcrops_bibliography, 
                                         find_duplicates(storagerootcrops_bibliography))
## Screen and filter by title
screen_titles(storagerootcrops_unique)
storagerootcrops_st <- read_csv("storagerootcrops_st.csv")
storagerootcrops_st <- storagerootcrops_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
storagerootcrops_st$abstract
screen_abstracts(storagerootcrops_st%>% as.data.frame())  

storagerootcrops_final <- read_csv("storagerootcrops_sa.csv")
storagerootcrops_final <- storagerootcrops_final %>% filter(!screened_abstracts == "excluded")
```

## Legumes
```{r}
legumes_bibliography <- read_bibliography(c("../Data/ScienceDirect_legumes.ris",  #ScienceDirect
                                         "../Data/scopus_legumes.ris",  # Scopus
                                         "../Data/WebofScience_legumes.ciw")) # Web of science
## Remove duplicates
legumes_unique <- extract_unique_references(legumes_bibliography, 
                                         find_duplicates(legumes_bibliography))
## Screen and filter by title
screen_titles(legumes_unique)
legumes_st <- read_csv("legumes_st.csv")
legumes_st <- legumes_st %>% filter(!screened_titles == "excluded")

## Screen and filter by abstract
legumes_st$abstract
screen_abstracts(legumes_st%>% as.data.frame())  

legumes_final <- read_csv("legumes_sa.csv")
legumes_final <- legumes_final %>% filter(!screened_abstracts == "excluded")
```

# Merge datasets

```{r}
Papers_database <- list(canola_oliseed_final %>% mutate(Crop = "Canola"), 
                        corn_final %>% mutate(Crop= "Corn"), 
                        cotton_final %>% mutate(Crop= "Cotton"), 
                        grasses_final %>% mutate(Crop= "Grasses"), 
                        legumes_final %>% mutate(Crop= "Legumes"), 
                        potato_final %>% mutate(Crop= "Potato"), 
                        rice_final %>% mutate(Crop= "Rice"), 
                        sorghum_final %>% mutate(Crop= "Sorghum"),
                        storagerootcrops_final %>% mutate(Crop= "Storageroots"),
                        sugarcane_final %>% mutate(Crop= "Suguarcane"), 
                        sunflower_final %>% mutate(Crop= "Sunflower"), 
                        wheat_final %>% mutate(Crop= "Wheat")) %>% 
  map(.f = ~dplyr::select(.x,c(Crop, label, type, title, author, journal, 
                               issue, volume, doi, url,source,
                               screened_abstracts, screened_titles)))  %>% 
  map(.f = ~mutate(.x, issue = as.character(issue)))  %>% 
  map(.f = ~mutate(.x, volume = as.character(volume)))  %>% 
  bind_rows() %>% 
  rowid_to_column()
```

# Data extraction

After filtering the papers, the final step involves opening each paper, screening the figures, and saving each figure in a folder. The figures should be labeled with the paper's ID number and the corresponding figure number. Next, use the juicr package in R to upload the images, and extract the data points from each figure.

The code below is one example

```{r}
## Paper 141 (wheat paper)
GUI_juicr("../../Data/Figures/141_Fig2a_juicr.png")
GUI_juicr("../../Data/Figures/141_Fig2b.png")
GUI_juicr("../Data/Figures/141_Fig2_c.png")
GUI_juicr("../Data/Figures/141_Fig2_d.png")

## paper 142 (wheat paper)
GUI_juicr("../../Data/Figures/142_Fig2_a")
GUI_juicr("../Data/Figures/142_Fig2_b.png")
GUI_juicr("../Data/Figures/142_Fig2_c")
GUI_juicr("../Data/Figures/142_Fig2_d.png")
```

